diffusion, websites with 1 pc

### 2023-03-22 paper/submission1/tranos2023_backup.qmd
lisa maps titles

---
title: "Digital economy in the UK: a multi-scalar story of the diffusion of web technologies"
author:
  - name: Emmanouil Tranos
    email: e.tranos@bristol.ac.uk
    affiliations: 
      - id: some-tech
        name: University of Bristol and The Alan Turing Institute
        department: 
        address: 
        city: 
        state: State
        postal-code: UK
    corresponding: e.tranos@bristol.ac.uk
address:
  - attributes:
        corresponding: true
    note: This is the first author footnote.
abstract: |
  This paper maps the participation in the digital economy and its evolution in the UK over space and time. Most of the existing economic geography literature which dealt with the spatiality of the internet employed supply-side measures, such as infrastructural capacity, in order to understand the geography of the digital economy and its potential spatial economic effects. Useful as these approaches might have been, they cannot capture the micro-processes and the characteristics of the individual online behaviour. Using large volumes of archived and geolocated web content, this paper models the diffusion of web technologies over space and time in the UK. The data and geolocation strategy allow to capture these processes at a very granular spatial scale. The modelling approach, which is based on simple spatial analytical methods and on the estimation of diffusion curves at various scales, enables to depict the role of geography and other cognitive factors which drove the diffusion of web technologies. Although the focus is on a recent historical period -- 1996-2012 -- the results of the analysis depict diffusion mechanisms which can be very useful in understanding the evolutionary patterns of the adoption of other newer technologies.
keywords: 
  - keyword1
  - keyword2
date: last-modified
bibliography: bibliography
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal Name
      formatting: preprint
      model: 3p
      cite-style: authoryear
editor: 
  markdown: 
    wrap: 72
---

>>>>

---
title: "Digital economy in the UK: a multi-scalar story of the diffusion of web technologies"
author:
  - name: Emmanouil Tranos
    email: e.tranos@bristol.ac.uk
    affiliations: 
      - id: some-tech
        name: University of Bristol and The Alan Turing Institute
        department: 
        address: 
        city: 
        state: State
        postal-code: UK
    corresponding: e.tranos@bristol.ac.uk
address:
  - attributes:
        corresponding: true
    note: This is the first author footnote.
abstract: |
  This paper maps the participation in the digital economy and its evolution in the UK over space and time. Most of the existing economic geography literature which dealt with the spatiality of the internet employed supply-side measures, such as infrastructural capacity, in order to understand the geography of the digital economy and its potential spatial economic effects. Useful as these approaches might have been, they cannot capture the micro-processes and the characteristics of the individual online behaviour. Using large volumes of archived and geolocated web content, this paper models the diffusion of web technologies over space and time in the UK. The data and geolocation strategy allow to capture these processes at a very granular spatial scale. The modelling approach, which is based on simple spatial analytical methods and on the estimation of diffusion curves at various scales, enables to depict the role of geography and other cognitive factors which drove the diffusion of web technologies. Although the focus is on a recent historical period -- 1996-2012 -- the results of the analysis depict diffusion mechanisms which can be very useful in understanding the evolutionary patterns of the adoption of other newer technologies.
keywords: 
  - keyword1
  - keyword2
date: last-modified
bibliography: bibliography.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal Name
      formatting: preprint
      model: 3p
      cite-style: super
editor: 
  markdown: 
    wrap: 72
---

### 2023-03-22 src/level_lisa_la.Rmd
lisa maps titles

map <- tm_shape(mun_merge_new) + tm_fill(col = "quadrant", breaks = breaks, 
                                         palette = c("white","red","blue",
                                                     rgb(0,0,1,alpha=0.4),
                                                     rgb(1,0,0,alpha=0.4)), 
                                         labels = c("Not significant", "High-High","Low-Low","Low-High","High-Low"), 
                                         title="LISA for level, LA") +
  tm_legend(text.size = 1) +
  #tm_scale_bar(position = c("LEFT", "BOTTOM"),text.size = 1.0)+
  #tm_compass(type = "8star",   position = c("RIGHT", "BOTTOM"),      show.labels = 2,   text.size = 0.5)+
  #tm_borders(alpha=.1) +
  tm_borders(lwd = 0) +
  tm_shape(la, simplify = .2) + tm_borders(alpha=1, lwd = .7) +
  tm_shape(tif_sf) + tm_dots() + tm_text("name", size = .5) +
  tm_layout( frame = FALSE,  title = t) #"LISA with the R p-values ")
tmap_save(map, filename = paste(path.out, t, ".png", sep = ""))
}

@@

map <- tm_shape(mun_merge_new, projection = "+init=epsg:4326") + tm_fill(col = "quadrant", breaks = breaks, 
                                         palette = c("white","red","blue",
                                                     rgb(0,0,1,alpha=0.4),
                                                     rgb(1,0,0,alpha=0.4)), 
                                         labels = c("Not significant", "High-High","Low-Low","Low-High","High-Low"), 
                                         title="LISA for level, LA") +
  tm_legend(text.size = 1) +
  #tm_scale_bar(position = c("LEFT", "BOTTOM"),text.size = 1.0)+
  #tm_compass(type = "8star",   position = c("RIGHT", "BOTTOM"),      show.labels = 2,   text.size = 0.5)+
  #tm_borders(alpha=.1) +
  tm_borders(lwd = 0) +
  tm_shape(la, simplify = .2) + tm_borders(alpha=1, lwd = .7) +
  tm_shape(tif_sf) + tm_dots() + tm_text("name", size = .5) +
  tm_layout( frame = FALSE,  title = t) #"LISA with the R p-values ") +
tmap_options(check.and.fix = TRUE)
tmap_save(map, filename = paste(path.out, t, ".png", sep = ""))
                                     }

>>>>

map <- tm_shape(mun_merge_new) + tm_fill(col = "quadrant", breaks = breaks, 
                                         palette = c("white","red","blue",
                                                     rgb(0,0,1,alpha=0.4),
                                                     rgb(1,0,0,alpha=0.4)), 
                                         labels = c("Not significant", "High-High","Low-Low","Low-High","High-Low"), 
                                         title="LISA, websites per firm in a LA") +
  tm_legend(text.size = 1) +
  #tm_scale_bar(position = c("LEFT", "BOTTOM"),text.size = 1.0)+
  #tm_compass(type = "8star",   position = c("RIGHT", "BOTTOM"),      show.labels = 2,   text.size = 0.5)+
  #tm_borders(alpha=.1) +
  tm_borders(lwd = 0) +
  tm_shape(la, simplify = .2) + tm_borders(alpha=1, lwd = .7) +
  tm_shape(tif_sf) + tm_dots() + tm_text("name", size = .5) +
  tm_layout( frame = FALSE,  title = t) #"LISA with the R p-values ")
tmap_save(map, filename = paste(path.out, t, ".png", sep = ""))
}

@@

map <- tm_shape(mun_merge_new, projection = "+init=epsg:4326") + tm_fill(col = "quadrant", breaks = breaks, 
                                         palette = c("white","red","blue",
                                                     rgb(0,0,1,alpha=0.4),
                                                     rgb(1,0,0,alpha=0.4)), 
                                         labels = c("Not significant", "High-High","Low-Low","Low-High","High-Low"), 
                                         title="LISA, websites per firm in a LA") +
  tm_legend(text.size = 1) +
  #tm_scale_bar(position = c("LEFT", "BOTTOM"),text.size = 1.0)+
  #tm_compass(type = "8star",   position = c("RIGHT", "BOTTOM"),      show.labels = 2,   text.size = 0.5)+
  #tm_borders(alpha=.1) +
  tm_borders(lwd = 0) +
  tm_shape(la, simplify = .2) + tm_borders(alpha=1, lwd = .7) +
  tm_shape(tif_sf) + tm_dots() + tm_text("name", size = .5) +
  tm_layout( frame = FALSE,  title = t) #"LISA with the R p-values ") +
tmap_options(check.and.fix = TRUE)
tmap_save(map, filename = paste(path.out, t, ".png", sep = ""))
                                     }
